On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-07-17 docs/mvfits_paper/mvf.tex

is the \textit{pseudo-inverse} of $\hatU$.

@@

\par While it is tempting to embrace \eqn{eq:rat1}'s $f({\vec{x}})$ as a nonlinear function and so resort to nonlinear modeling methods, a reformulation reveals an underlying linear structure.

>>>>

is the \textit{pseudo-inverse} \cite{Moore1920,Penrose:1955} of $\hatU$.

@@

\par While it is tempting to embrace \eqn{eq:rat1}'s $f({\vec{x}})$ as a nonlinear function and so resort to nonlinear modeling methods, a reformulation reveals an underlying linear structure \cite{Press:1992:NRC:148286}.
